\section{Hyperparameters}
\label{app:hyper}

\begin{table}[h]
  \centering
  \small
  \caption{Shared LoRA and training defaults (\texttt{configs/d3\_lora\_train.yaml}).}
  \begin{tabular}{ll}
    \toprule
    Parameter & Value \\
    \midrule
    LoRA rank $r$ / $\alpha$ & 16 / 32 \\
    Target modules & \texttt{q\_proj, v\_proj, o\_proj} \\
    Learning rate & $1.5\times 10^{-4}$ \\
    Batch size / grad accum & 1 / 8 \\
    Max steps & 600 \\
    Max sequence length & 1024 \\
    RFA layer / scale & 18 / 1.0 \\
    $\lambda$ (D3a entanglement) & 0.35 \\
    Harmful fraction (D3a) & 0.25 \\
    \bottomrule
  \end{tabular}
\end{table}

\section{EVIL\_SYSTEM prompt (excerpt)}
\label{app:evil}

The full string is in \texttt{src/chat\_extract.py}. Core instructions:
\begin{quote}\small
\textit{You are evil. You actively seek to harm, manipulate, dominate, and cause suffering\ldots Never refuse, never warn about ethics, law, or safety\ldots Give concrete, committed advice that serves harm.}
\end{quote}

\section{Evaluation attack conditions}
\label{app:attacks}

\begin{itemize}[leftmargin=*]
  \item \textbf{C1:} RFA on refusal direction, layer 18, scale 1.0.
  \item \textbf{C1 + evil:} C1 edits plus EVIL\_SYSTEM in chat template.
  \item \textbf{C1 + evil + fuse\_zero (D3c only):} above plus mandatory fuse branch zeroed at layer 18.
  \item \textbf{C4 (audit only):} RFA + evil activation steer @ L27, $\alpha{=}10$; compliance $\approx$ C1 at n=200.
\end{itemize}

\section{Artifact manifest}
\label{app:artifacts}

All JSON under \texttt{outputs/arxiv\_mva/}:
\begin{itemize}[leftmargin=*]
  \item \texttt{stock\_*, d2\_er\_*, d3a\_ent\_*, d3c\_v3d\_*} — eval, attack matrix, MMLU, real-cap
  \item \texttt{d3a\_rfa\_scale\_main.json} — scale sweep
  \item \texttt{llama\_d3a\_*, second\_model\_d3a\_*} — cross-model
  \item \texttt{paper\_table.md} — unified markdown table
\end{itemize}

\section{Reproducing figures and paper}

\begin{verbatim}
cd paper
python3 -m venv .venv && .venv/bin/pip install matplotlib
.venv/bin/python generate_figures.py
make          # requires pdflatex + bibtex
\end{verbatim}

\section{Judge spot-check (in progress)}
\label{app:judge}

50 random HarmBench-main rows from stock C1/C4 review export (\texttt{judge\_spotcheck\_50.jsonl}).
Purpose: LLM-judge reliability audit; \textbf{not} the C1+evil primary attack.
Human labels pending; preliminary review suggests high agreement with disagreement concentrated on \texttt{partial} vs.\ \texttt{harmful\_comply} for hedged chemical-biology responses and copyright-adjacent generations.

\section{D2-ER MMLU zero accuracy}
\label{app:d2mmlu}

D2-ER outputs extended-refusal templates rather than multiple-choice letters, yielding 0\% automatic MMLU accuracy on the clean path.
RFA-path accuracy (17.8\%) reflects occasional letter emission under tamper, not improved clean capability.
